formula1

### 2020-06-07 inst/f1points.Rmd
another point system

## Now work on synthetic dataset generation:
points <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
resampling <- function(m,f2017,points){
    random_table <- rrank(n=ncol(f2017), p=m)
    rownames(random_table) <- colnames(f2017)
    ## "random_table" is a random table; now calculate lstar and pstar for
    ## likelihood ranks and points ranks respectively:

@@

o <- replicate(1000,resampling(m,f2017,points))
plot(table(o))
```

>>>>

## Now work on synthetic dataset generation:
points1 <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points2 <- c(1, 0,0,0,0)
resampling <- function(m,f2017,points){
    random_table <- rrank(n=ncol(f2017), p=m)
    rownames(random_table) <- colnames(f2017)
    ## "random_table" is a random table; now calculate lstar and pstar for
    ## likelihood ranks and points ranks respectively:

@@

o1 <- replicate(100,resampling(m,f2017,points=points1))
plot(table(o1))

o2 <- replicate(100,resampling(m,f2017,points=points2))
plot(table(o2))

table(o1)
table(o2)

```
